Domain-specific working memory loads selectively increase negative interpertations of surprised facial expressions

### 2019-08-15 Manuscript/Manuscript.tex
Updating analyses and markdown
Finalizing results section

We used R (Version 3.6.0; {\textbf{???}}) and the R-packages * \}dplyr* {[}@ \}R-dplyr{]}, \emph{broom} (Version 0.5.2; {\textbf{???}}), \emph{forcats} (Version 0.4.0; {\textbf{???}}), \emph{ggplot2} (Version 3.1.1; {\textbf{???}}), \emph{lattice} (Version 0.20.38; {\textbf{???}}), \emph{openxlsx} (Version 4.1.0; {\textbf{???}}), \emph{papaja} (Version 0.1.0.9842; {\textbf{???}}), \emph{plyr} (Version 1.8.4; @ \}R-dplyr; {\textbf{???}}), \emph{purrr} (Version 0.3.2; {\textbf{???}}), \emph{readr} (Version 1.3.1; {\textbf{???}}), \emph{readxl} (Version 1.3.1; {\textbf{???}}), \emph{Rmisc} (Version 1.5; {\textbf{???}}), \emph{stringr} (Version 1.4.0; {\textbf{???}}), \emph{tibble} (Version 2.1.3; {\textbf{???}}), \emph{tidyr} (Version 0.8.3.9000; {\textbf{???}}), and \emph{tidyverse} (Version 1.2.1; {\textbf{???}}) for all our analyses. Data preprocessing was completed in R using the mousetrap package ({\textbf{???}}). First, percent negative ratings were calculated for happy, angry, and surprised faces across all trial types, as well as a percent correct score for the memory probe trials. After, trials were screened for RT outliers. Any trials that were greater than three standard deviations from the mean were removed from the analyses. Additionally, we removed the preceding face rating trial for any incorrect memory probe trials, as these trials can be considered a manipulation failure.

@@

Distributions of ratings were first tested for normality using Shapiro-Wilk's test. The results of all four tests were highly significant (p's \textless{} .001), so non-parametric tests were used for data analysis. Friedman's test results showed significantly different distributions across the conditions \(\chi^{2}\)(3.00) = 27.41, p \textless{} .001. Follow up Wilcoxon signed rank tests revealed that surprise is rated as more negative when holding emotional content in working memory compared to neutral content. Low emotional load ratings were significantly more negative than low, Z = 3.31, p = .001, neutral and high, Z = 3.62, p \textless{} .001, neutral loads. The same was true for high emotional load ratings and low, Z = 4.52, p \textless{} .001, and high, Z = 3.72, p \textless{} .001, neutral loads. However, there was no discernable effect of load. That is, the comparisons between low and high load ratings for both emotional, Z = -1.10, p = .273, and neutral, Z = -0.03, p = .975, load ratings were not significantly different.\footnote{These results are qualitatively the same when analyzing these data with a repeated measures ANOVA.}

@@

To assess for normality, the data were first tested with Shapiro-Wilk's test. Two conditions did not appear to be sampled from normal distributions, so non-parametric tests were used. Overall, there was a trending difference across the four conditions, \(\chi^{2}\)(3.00) = 7.15, p .067. Wilcoxon signed rank tests were used to assess post-hoc comparisons and Bonferroni corrected p-value = 0.01. While none of the post-hoc comparisons reached the adjusted significance level, there was a trending difference between emotional and neutral RTs in the high load condition, Z = 2.51, p = .012, such that high emotional WM loads had slower RTs. Two other comparisons were trending for traditional levels of significance. Low emotional WM loads tended to take marginally longer than high neutral WM loads, Z = 1.96, p = .050, and low neutral WM loads took marginally longer than high neutral WM laods, Z = -1.75, p = 0.08. All other comparisons were not significant.

@@

Next, we tested for reaciton time differences between positive and negative interpretations of surprised facial expressions within each working memory load condition. Given the non-normality of these data, we used paired-sample Wilcoxon signed rank tests for assessing differences between positive and negative ratings of surprise RTs. This difference was significant \emph{only} for the low emotional load trials, with surprise rated as positive taking signficantly longer than surprise rated as negative (.009). All other comparisons were not significant (p's \textgreater{} .200). Further, this effect survived Bonferroni correction (p = .012).

@@

Finally, we assessed differences in maximum absolute deviation (MAD) across the WM trial conditions.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

The effect of high vs.~low load is still not apparent in these data, just like Mattek et al.~2016. An alternative explanation is that the high load manipulation is not sufficiently difficult to recruit the targeted cognitive resources; however, future work will be needed to better test this alternative.

>>>>

We used R (Version 3.6.0; {\textbf{???}}) and the R-packages * \}dplyr* {[}@ \}R-dplyr{]}, \emph{broom} (Version 0.5.2; {\textbf{???}}), \emph{forcats} (Version 0.4.0; {\textbf{???}}), \emph{ggplot2} (Version 3.1.1; {\textbf{???}}), \emph{lattice} (Version 0.20.38; {\textbf{???}}), \emph{mousetrap} (Version 3.1.2; {\textbf{???}}), \emph{openxlsx} (Version 4.1.0; {\textbf{???}}), \emph{papaja} (Version 0.1.0.9842; {\textbf{???}}), \emph{plyr} (Version 1.8.4; @ \}R-dplyr; {\textbf{???}}), \emph{purrr} (Version 0.3.2; {\textbf{???}}), \emph{readr} (Version 1.3.1; {\textbf{???}}), \emph{readxl} (Version 1.3.1; {\textbf{???}}), \emph{Rmisc} (Version 1.5; {\textbf{???}}), \emph{stringr} (Version 1.4.0; {\textbf{???}}), \emph{tibble} (Version 2.1.3; {\textbf{???}}), \emph{tidyr} (Version 0.8.3.9000; {\textbf{???}}), and \emph{tidyverse} (Version 1.2.1; {\textbf{???}}) for all our analyses. Data preprocessing was completed in R using the mousetrap package ({\textbf{???}}). First, percent negative ratings were calculated for happy, angry, and surprised faces across all trial types, as well as a percent correct score for the memory probe trials. After, trials were screened for RT outliers. Any trials that were greater than three standard deviations from the mean were removed from the analyses. Additionally, we removed the preceding face rating trial for any incorrect memory probe trials, as these trials can be considered a manipulation failure.

@@

Distributions of ratings were first tested for normality using Shapiro-Wilk's test. The results of all four tests were highly significant (p's \textless{} .001), so non-parametric tests were used for data analysis. Friedman's test results showed significantly different distributions across the conditions \(\chi^{2}\)(3.00) = 27.79, p \textless{} .001. Follow up Wilcoxon signed rank tests revealed that surprise is rated as more negative when holding emotional content in working memory compared to neutral content. Low emotional load ratings were significantly more negative than low, Z = 3.27, p = .001, neutral and high, Z = 3.67, p \textless{} .001, neutral loads. The same was true for high emotional load ratings and low, Z = 4.55, p \textless{} .001, and high, Z = 3.81, p \textless{} .001, neutral loads. However, there was no discernable effect of load. That is, the comparisons between low and high load ratings for both emotional, Z = -1.35, p = .176, and neutral, Z = -0.06, p = .954, load ratings were not significantly different.\footnote{These results are qualitatively the same when analyzing these data with a repeated measures ANOVA.}

@@

To assses for normality, the data were first tested with Shapiro-Wilk's test. All conditions appeared to be sampled from normal distributions (p's \textgreater{} .08). A Load (Low, High) X Type (Neutral, Emotional) repeated measures ANOVA was used to assess differences in the RTs. There was a trend towards a main effect of type, F(1, 49) = 2.97, p = 0.09. However, follow up Wilcoxon signed rank tests did not reveal any differences that survived correction for multiple comparisons. There was a trend for RTs of face ratings on high load emotional trials to be longer than high load neutral trials (p =), and a similar pattern for low load emotional trial ratings to take longer than high load neutral trials (p = . One other comparison approached trend levels of signficance, with low load neutral trial ratings taking longer than high neutral loads, (p = . All other comparisons were non-significant (p's \textgreater{} .

@@

Next, we tested for reaction time differences between positive and negative interpretations of surprised facial expressions within each working memory load condition. Given the non-normality of these data, we used paired-sample Wilcoxon signed rank tests for assessing differences between positive and negative ratings of surprise RTs. This difference was significant \emph{only} for the low emotional load trials, with surprise rated as positive taking signficantly longer than surprise rated as negative (.009). All other comparisons were not significant (p's \textgreater{} .200). Further, this effect survived Bonferroni correction (p = .012).

@@

Finally, we assessed differences in maximum absolute deviation (MAD) across the WM trial conditions. While one of the conditions, low emotional MDs, was not normally distributed (p = .024), all other conditions were normally distributed and repeated-measures ANOVA was used to analyze the MDs across conditions. There was a significant effect of load, F(1.00,196.00) = 5.51, p = .020, such that MDs under high load were larger than trials with low load. There was no significant effect of domain on MDs, F(1.00 196.00) = 0.01, p = .912, nor an interaction of load by domain.
\# Discussion
The effect of high vs.~low load is still not apparent in these data, just like Mattek et al.~2016. An alternative explanation is that the high load manipulation is not sufficiently difficult to recruit the targeted cognitive resources; however, future work will be needed to better test this alternative.
